\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2012-10-24 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
fixed a file name in the manual
simplified the IBM BlueGene section

SPECFEM3D Cartesian includes coupled fluid-solid domains and
adjoint capabilities, which enables one to address seismological inverse problems, but for linear rheologies only so far.
To accommodate visco-plastic or non-linear rheologies, the reader can refer to
the \href{http://geoelse.stru.polimi.it/}{GeoELSE} software package \citep{CaGa97,StPaIg09,ChMoTsBaKrKaStKr10}.

@@

The SPECFEM3D Cartesian software package comes in a gzipped tar ball. In the
directory in which you want to install the package, type
\begin{lyxcode}
{\small tar~-zxvf~SPECFEM3D\_V2.1.0.tar.gz}{\small \par}
\end{lyxcode}
The directory \texttt{\small SPECFEM3D/} will then contain
the source code.\\

@@

\noindent
Then, to configure the code, for the SPECFEM3D\_GLOBE version type this:\\

@@

\noindent
and for SPECFEM3D\_Cartesian type this:\\

\noindent
\texttt{./configure FC=bgxlf90\_r MPIFC=mpixlf90\_r CC=bgxlc\_r LOCAL\_PATH\_IS\_ALSO\_GLOBAL=true}.\\

>>>>

SPECFEM3D Cartesian includes coupled fluid-solid domains and
adjoint capabilities, which enables one to address seismological inverse problems, but for linear rheologies only so far.
To accommodate visco-plastic or non-linear rheologies, the reader can refer to
the \href{http://geoelse.stru.polimi.it/}{GeoELSE} software package \citep{CaGa97,StPaIg09}.

@@

The SPECFEM3D Cartesian software package comes in a gzipped tar ball. In the
directory in which you want to install the package, type
\begin{lyxcode}
{\small tar~-zxvf~SPECFEM3D\_V2.1.0\_Cartesian.tar.gz}{\small \par}
\end{lyxcode}
The directory \texttt{\small SPECFEM3D/} will then contain
the source code.\\

@@

\noindent
Then, to configure the code, type this:\\

@@
